---
title: '240125'
author: "Arturo Bertero"
date: "2024-01-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Input

```{r}
#libraries
library(pacman)
p_load(tidyverse, janitor, here, haven, labelled, sjmisc, skimr,
       stargazer, IsingFit, qgraph, Matrix, igraph, NetworkComparisonTest, bootnet,
       rio, IsingSampler, compute.es, foreign, mgm, matrixcalc, openxlsx, Rcpp,
       forestplot, ggplot2, compute.es, jtools, glue, EGAnet, signnet, magick)

#remove scipen
options(scipen=999)
```

```{r}
#Import dataset
load(here("Input", "usa_data.RData"))
```

# Processing

## Create objects

```{r}
shortnames_22 = names(issp_2019_nodes)
shortnames_23 = names(issp_2019_anger)

longnames_22 <- c("Perception of large income inequality (p_income)",
            "Perception of tax regressivity (p_tax)",
            "Belief in progressive taxation (b_tax)",
            "Judgment of unfair distribution (j_income)",
            "Judgment of political distrust in redistribution (j_distrust)",
            "Judgment of failure of public redistribution (j_failure)",
            "Importance of wealthy family (e_weafam)",
            "Importance of parental education (e_edupar)",
            "Importance of education (e_edu)",
            "Importance of hard work (e_work)",
            "Importance of knowing right people (e_people)",
            "Importance of political connections (e_connec)",
            "Importance of giving bribes (e_bribes)",
            "Importance of race (e_race)",
            "Importance of religion (e_relig)",
            "Importance of sex (e_sex)",
            "Belief in public redistribution (b_public)",
            "Belief in market redistribution (b_market)",
            "Pay criteria, Responsibility (b_resp)",
            "Pay criteria, Training (b_train)",
            "Pay criteria, Need (b_need)",
            "Pay criteria, Merit (b_merit)")

legendnames_22 <- c("Perception of large income inequality",
            "Perception of tax regressivity",
            "Belief in progressive taxation",
            "Judgment of unfair distribution",
            "Judgment of political distrust in redistribution",
            "Judgment of failure of public redistribution",
            "Importance of wealthy family",
            "Importance of parental education",
            "Importance of education",
            "Importance of hard work",
            "Importance of knowing right people",
            "Importance of political connections",
            "Importance of giving bribes",
            "Importance of race",
            "Importance of religion",
            "Importance of sex",
            "Belief in public redistribution",
            "Belief in market redistribution",
            "Pay criteria: Responsibility",
            "Pay criteria: Training",
            "Pay criteria: Need",
            "Pay criteria: Merit")

```

```{r}

#remove haven labels
issp_2019_nodes = sapply(issp_2019_nodes, haven::zap_labels)
issp_2019_can = sapply(issp_2019_can, haven::zap_labels)
issp_2019_anger = sapply(issp_2019_anger, haven::zap_labels)

#Communities
ega_results <- EGA(
  data = issp_2019_nodes,
  method = "glasso",         # "glasso" for GGM estimation with graphical LASSO
  community_detection = "walktrap" # Default 
)

ega_results$wc

```

```{r}
#colors
ggm_groups = list(
 "Views on inequality"=c(1,2,3,4,5,6,17,18),
 "Mixed factors"=c(7,8,11,12,13,21),
 "Individualist factors"=c(9,10,19,20,22),
 "Structuralist factors"=c(14,15,16)
 )

# ega_colors <- c(
#   "#E41A1C", # Red
#   "#377EB8", # Blue
#   "#4DAF4A", # Green
#   "#984EA3", # Purple
#   "#FF7F00", # Orange
#   "#FFFF33", # Yellow
#   "#A65628", # Brown
#   "#F781BF"  # Pink
# )

ggm_colors <- c("#FBB4AE",  "#A6D9E0", "#CCEBC5", "#FDDA77")

```

## Full scale network

```{r}
#fit mgm
mgm_issp_2019_nodes = mgm(issp_2019_nodes, type = rep("g",22), 
              level = rep(1, 22), lambdaSel = "EBIC", ruleReg = "OR")


#predictability
pred_obj <- predict(object = mgm_issp_2019_nodes, 
                    data = issp_2019_nodes, 
                    errorCon = 'R2')

#descriptives
mgm_nodes_desc = as.vector(mgm_issp_2019_nodes$pairwise$wadj)
length(mgm_nodes_desc[mgm_nodes_desc != 0])/462


pred_df = pred_obj$errors %>% 
  arrange(R2)
```

```{r}
#plot
set.seed(100)
GraphMGM<-qgraph(mgm_issp_2019_nodes$pairwise$wadj, layout = 'spring',
            labels = shortnames_22, nodeNames = legendnames_22,  
            groups = ggm_groups, color = ggm_colors, 
            legend=T, legend.cex = 0.33, 
            label.scale = F, label.cex = 0.7,
            edge.color=mgm_issp_2019_nodes$pairwise$edgecolor_cb,
            borders = T, vsize=7.0, esize = 15, GLratio = 2,
            pie = pred_obj$errors[,2], pieColor = rep('gray50',22),
            filetype="jpg", filename=here("Output", "Fig_1"))

# PDF
set.seed(100)
GraphMGM<-qgraph(mgm_issp_2019_nodes$pairwise$wadj, layout = 'spring',
            labels = shortnames_22, nodeNames = legendnames_22,  
            groups = ggm_groups, color = ggm_colors, 
            legend=T, legend.cex = 0.33, 
            label.scale = F, label.cex = 0.7,
            edge.color=mgm_issp_2019_nodes$pairwise$edgecolor_cb,
            borders = T, vsize=7.0, esize = 15, GLratio = 2,
            pie = pred_obj$errors[,2], pieColor = rep('gray50',22),
            filetype="pdf", filename=here("Output", "PDF", "Fig_1"))
            

# Open EPS device
postscript(file = here("Output", "EPS", "Fig_1.eps"), 
           width = 10, height = 6, 
           horizontal = FALSE, 
           paper = "special", 
           onefile = FALSE)

# Plot the graph
set.seed(100)
GraphMGM <- qgraph(
  mgm_issp_2019_nodes$pairwise$wadj, 
  layout = 'spring',
  labels = shortnames_22, 
  nodeNames = legendnames_22,  
  groups = ggm_groups, 
  color = ggm_colors, 
  legend = TRUE, 
  legend.cex = 0.33, 
  label.scale = FALSE, 
  label.cex = 0.7,
  edge.color = mgm_issp_2019_nodes$pairwise$edgecolor_cb,
  borders = TRUE, 
  vsize = 7.0, 
  esize = 15, 
  GLratio = 2,
  pie = pred_obj$errors[,2], 
  pieColor = rep('gray50', 22)
)

# Close the device
dev.off()
```

### H1: Small world 

```{r}
# ITA_small_core = qgraph::smallworldness(CANFit$weiadj, B = 1000)

(small_w = NetworkToolbox::smallworldness(mgm_issp_2019_nodes$pairwise$wadj, iter = 1000, 
          progBar = FALSE, method = c("TJHBL")))

#ASPL
NetworkToolbox::pathlengths(mgm_issp_2019_nodes$pairwise$wadj, weighted = FALSE)

#Clustering
NetworkToolbox::transitivity(mgm_issp_2019_nodes$pairwise$wadj, weighted = FALSE)
```

### H2: Centrality

```{r}
#centrality
centrality_mgm_graph = centralityPlot(GraphMGM, labels = longnames_22, 
                                      orderBy = "Strength", 
                                      scale = "z-scores")

centrality_mgm_graph = centrality_mgm_graph +  
  geom_vline(xintercept=0, linetype="dotted") +
  scale_x_continuous(limits = c(-2,3), breaks = c(-2,-1,0,1,2,3)) +
  # theme_nice() +
  theme(axis.text.y=element_text(hjust=1))

ggsave(here("Output", "Fig_2.jpg"), centrality_mgm_graph,
        height = 4)

# Save as EPS
ggsave(here("Output", "EPS", "Fig_2.eps"), 
       centrality_mgm_graph,
       height = 4, width = 10, 
       dpi = 600, 
       device = cairo_ps)

# Save as pdf
ggsave(here("Output", "PDF", "Fig_2.pdf"), 
       centrality_mgm_graph,
       height = 4, width = 8, 
       dpi = 600, 
       device = pdf)

```


## Moderation by anger

```{r}
#Fit moderated ggm
mgm_mod <- mgm(data = issp_2019_anger,
               type = rep("g", 23),
               level = rep(1, 23),
               lambdaSel = "CV",
               ruleReg = "OR",
               moderators = 23, 
               threshold = "none", 
               pbar = FALSE)
```


```{r}
#Inspect interaction parameters [comments are wrong:readapt]
mgm_mod$interactions$indicator
#45 pairwise interactions
#27 3-way interactions (moderation)

#acces a pairwise interaction between variables 1 (p_ineq) and 3 (p_tax) can be obtained like this:
showInteraction(object = mgm_mod, int = c(1,22))

#access a 3-way interaction
showInteraction(object = mgm_mod, int = c(1,22,23))

#redis_f redis_p = 0.025
#mod = 0.064
# if anger 0, redis_f redis_p = 0.025 + 0.064 * 0 = 0.025
# if anger 3, redis_f redis_p = 0.025 + 0.064 * 3 = 0.217
# if anger 7, redis_f redis_p = 0.025 + 0.064 * 7 = 0.473
# if anger 10, redis_f redis_p = 0.025 + 0.064 * 10 = 0.665

#family sex = 0.065
#mod = 0.041
# if anger 0, family sex= 0.065 + 0.041 * 0 = 0.065
# if anger 10,family sex = 0.065 + 0.041 * 10 = 0.475

#edu redis_m = 0.009
#mod = 0.026
# if anger 0, edu redis_m= 0.009 + 0.026 * 0 = 0.009
# if anger 10,edu redis_m = 0.009 + 0.026 * 10 = 0.269

#edupar race = 0.0
#mod = -0.030
# if anger 0, edupar race = 0.0 -0.030 * 0 = 0.0
# if anger 10,edupar race = 0.0 -0.030 * 10 = -0.300

#edu bribes = 0
#mod = -0.018
# if anger 0, edu bribes = -0.018 +0.040  * 0 = -0.018
# if anger 10,edu bribes = -0.018 -0.040  * 10 = -0.418

#family connec = 0.145
#mod = 0.032
# if anger 0, edu bribes = 0.145 + 0.032 * 0 = 0.145
# if anger 10,edu bribes = 0.145 + 0.032 * 10 = 0.465

#ineq_p merit = 0.010
#mod = 0.011
# if anger 0, ineq_p merit = 0.010+ 0.011* 0 = 0.010
# if anger 3, ineq_p merit = 0.010+ 0.011* 3 = 0.043
# if anger 7, ineq_p merit = 0.010+ 0.011* 7 = 0.087
# if anger 10,ineq_p merit  =0.010 +0.011 * 10 = 0.120
```

```{r}
#access scale of anger (every variable is mean-centered and sd=1)
tb <- table(scale(issp_2019_anger[,23]))
names(tb) <- round(as.numeric(names(tb)), 2)
barplot(tb, axes=FALSE, xlab="", ylim=c(0, 250))
axis(2, las=2, c(0, 50, 100, 150, 200, 250))

```

```{r}
#conditioning on the moderator, interesting values are 0, 3, 7, 10 of v 11 (anger)
cond0 <- condition(object = mgm_mod, 
                   values = list('23' = 0))

cond3 <- condition(object = mgm_mod, 
                   values = list('23' = 3))

cond7 <- condition(object = mgm_mod, 
                   values = list('23' = 7))

cond10 <- condition(object = mgm_mod, 
                   values = list('23' = 10))

#these are now 3 different pairwise models, in which anger is fixed at 3 diff values
```

```{r}

cond0wadj = cond0$pairwise$wadj[1:22,1:22]
cond3wadj = cond3$pairwise$wadj[1:22,1:22]
cond7wadj = cond7$pairwise$wadj[1:22,1:22]
cond10wadj = cond10$pairwise$wadj[1:22,1:22]

walktrap_ega0 <- community.detection(
  network = cond0wadj,         # The GGM matrix
  method = "walktrap"            # Specify Walktrap for community detection
)

walktrap_ega3 <- community.detection(
  network = cond3wadj,         # The GGM matrix
  method = "walktrap"            # Specify Walktrap for community detection
)

walktrap_ega7 <- community.detection(
  network = cond7wadj,         # The GGM matrix
  method = "walktrap"            # Specify Walktrap for community detection
)

walktrap_ega10 <- community.detection(
  network = cond10wadj,         # The GGM matrix
  method = "walktrap"            # Specify Walktrap for community detection
)

walktrap_ega0
walktrap_ega3
walktrap_ega7
walktrap_ega10
```

```{r}
#colors
ggm_groups0 = list(
  "Community 1" = c(1, 2, 3, 4, 5, 6, 17, 18),
  "Community 2" = c(7, 11, 12, 13, 21),
  "Community 3" = c(8, 9, 10, 19, 20, 22),
  "Community 4" = c(14, 15, 16)
)

ggm_groups3 = list(
  "Community 1" = c(1, 2, 3, 4, 5, 6, 17, 18, 21),
  "Community 2" = c(7, 8, 9, 10, 11, 12, 13),
  "Community 3" = c(19, 20, 22),
  "Community 4" = c(14, 15, 16)
)


ggm_groups7 = list(
  "Community 1" = c(1, 2, 3, 4, 5, 6, 17, 21),
  "Community 2" = c(7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 18, 22),
  "Community 3" = c(19, 20)
)


ggm_groups10 = list(
  "Community 1" = c(1, 2, 3, 4, 5, 6, 17, 21),
  "Community 2" = c(7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 18, 22),
  "Community 3" = c(19, 20)
)


# ega_colors <- c(
#   "#E41A1C", # Red
#   "#377EB8", # Blue
#   "#4DAF4A", # Green
#   "#984EA3", # Purple
#   "#FF7F00", # Orange
#   "#FFFF33", # Yellow
#   "#A65628", # Brown
#   "#F781BF"  # Pink
# )
```

```{r}
# Fix colors for grey edges
edge_col0 <- ifelse(cond0$pairwise$edgecolor_cb == "darkgrey", "darkblue", cond0$pairwise$edgecolor_cb)
edge_col3 <- ifelse(cond3$pairwise$edgecolor_cb == "darkgrey", "darkblue", cond3$pairwise$edgecolor_cb)
edge_col7 <- ifelse(cond7$pairwise$edgecolor_cb == "darkgrey", "darkblue", cond7$pairwise$edgecolor_cb)
edge_col10 <- ifelse(cond10$pairwise$edgecolor_cb == "darkgrey", "darkblue", cond10$pairwise$edgecolor_cb)


#plot with 3 levels and fixed layout
Graph_cond_0 = qgraph(cond0$pairwise$wadj)
Graph_cond_3 = qgraph(cond3$pairwise$wadj)
Graph_cond_7 = qgraph(cond7$pairwise$wadj)
Graph_cond_10 = qgraph(cond10$pairwise$wadj)

#multiplot
jpeg(here("Output", "Fig_3.jpg"), 
    height = 12000, width = 12000, quality = 1000)

L<-averageLayout(Graph_cond_0, Graph_cond_3, Graph_cond_7, Graph_cond_10, layout = "spring")
lmat <- matrix(1:4, 2)
lo <- layout(lmat, width = c(1, 1))

set.seed(1)
Graph_cond_0 = qgraph(Graph_cond_0, layout = L,
            labels = shortnames_23,
            groups = ggm_groups0, color = ggm_colors, 
            legend=F, title = "Anger = 0", title.cex = 20,
            label.scale = F, label.cex = 11,
            edge.color=edge_col0,
            borders =  T, esize = 20, vsize = 10
)


set.seed(1)
Graph_cond_7 = qgraph(Graph_cond_7, layout = L,
            labels = shortnames_23,
            groups = ggm_groups7, color = ggm_colors, 
            legend=F, title = "Anger = 7", title.cex = 20,
            label.scale = F, label.cex = 11,
            edge.color=edge_col7,
            borders =  T, esize = 20, vsize = 10
)


set.seed(1)
Graph_cond_3 = qgraph(Graph_cond_3, layout = L,
            labels = shortnames_23,  
            groups = ggm_groups3, color = ggm_colors, 
            legend=F, title = "Anger = 3", title.cex = 20,
            label.scale = F, label.cex = 11,
            edge.color=edge_col3,
            borders =  T, esize = 20, vsize = 10
)

set.seed(1)
Graph_cond_10 = qgraph(Graph_cond_10, layout = L,
            labels = shortnames_23,  
            groups = ggm_groups10, color = ggm_colors, 
            legend=F, title = "Anger = 10", title.cex = 20,
            label.scale = F, label.cex = 11,
            edge.color=edge_col10,
            borders =  T, esize = 20, vsize = 10
)

dev.off()
```
```{r}
# Save in EPS

# Open EPS device
postscript(file = here("Output", "EPS", "Fig_3.eps"), 
           width = 23, height = 23, 
           horizontal = FALSE, 
           paper = "special", 
           onefile = FALSE)

# Shared layout
set.seed(1)
L <- averageLayout(Graph_cond_0, Graph_cond_3, Graph_cond_7, Graph_cond_10, layout = "spring")
lmat <- matrix(1:4, 2)
layout(lmat, widths = c(1, 1), heights = c(1, 1))

# Plot each graph
Graph_cond_0 <- qgraph(Graph_cond_0, layout = L,
                       labels = shortnames_23,
                       groups = ggm_groups0, color = ggm_colors, 
                       legend = FALSE, title = "Anger = 0", title.cex = 2.5,
                       label.scale = FALSE, label.cex = 1.4,
                       edge.color = edge_col0,
                       borders = TRUE, esize = 20, vsize = 10)

Graph_cond_3 <- qgraph(Graph_cond_3, layout = L,
                       labels = shortnames_23,
                       groups = ggm_groups3, color = ggm_colors, 
                       legend = FALSE, title = "Anger = 3", title.cex = 2.5,
                       label.scale = FALSE, label.cex = 1.4,
                       edge.color = edge_col3,
                       borders = TRUE, esize = 20, vsize = 10)

Graph_cond_7 <- qgraph(Graph_cond_7, layout = L,
                       labels = shortnames_23,
                       groups = ggm_groups7, color = ggm_colors, 
                       legend = FALSE, title = "Anger = 7", title.cex = 2.5,
                       label.scale = FALSE, label.cex = 1.4,
                       edge.color = edge_col7,
                       borders = TRUE, esize = 20, vsize = 10)

Graph_cond_10 <- qgraph(Graph_cond_10, layout = L,
                        labels = shortnames_23,
                        groups = ggm_groups10, color = ggm_colors, 
                        legend = FALSE, title = "Anger = 10", title.cex = 2.5,
                        label.scale = FALSE, label.cex = 1.4,
                        edge.color = edge_col10,
                        borders = TRUE, esize = 20, vsize = 10)

# Close the EPS device
dev.off()
```
```{r}
# Save in PDF

#multiplot
pdf(here("Output", "PDF", "Fig_3.pdf"), 
    height = 200, width = 200)

L<-averageLayout(Graph_cond_0, Graph_cond_3, Graph_cond_7, Graph_cond_10, layout = "spring")
lmat <- matrix(1:4, 2)
lo <- layout(lmat, width = c(1, 1))

set.seed(1)
Graph_cond_0 = qgraph(Graph_cond_0, layout = L,
            labels = shortnames_23,
            groups = ggm_groups0, color = ggm_colors, 
            legend=F, title = "Anger = 0", title.cex = 20,
            label.scale = F, label.cex = 11,
            edge.color=edge_col0,
            borders =  T, esize = 20, vsize = 10
)


set.seed(1)
Graph_cond_7 = qgraph(Graph_cond_7, layout = L,
            labels = shortnames_23,
            groups = ggm_groups7, color = ggm_colors, 
            legend=F, title = "Anger = 7", title.cex = 20,
            label.scale = F, label.cex = 11,
            edge.color=edge_col7,
            borders =  T, esize = 20, vsize = 10
)


set.seed(1)
Graph_cond_3 = qgraph(Graph_cond_3, layout = L,
            labels = shortnames_23,  
            groups = ggm_groups3, color = ggm_colors, 
            legend=F, title = "Anger = 3", title.cex = 20,
            label.scale = F, label.cex = 11,
            edge.color=edge_col3,
            borders =  T, esize = 20, vsize = 10
)

set.seed(1)
Graph_cond_10 = qgraph(Graph_cond_10, layout = L,
            labels = shortnames_23,  
            groups = ggm_groups10, color = ggm_colors, 
            legend=F, title = "Anger = 10", title.cex = 20,
            label.scale = F, label.cex = 11,
            edge.color=edge_col10,
            borders =  T, esize = 20, vsize = 10
)

dev.off()
```


```{r}
#descriptives of MNM: mean edge value
cond0_desc = cond0$pairwise$wadj[-23, ] 
cond0_desc = cond0_desc[, -23] 
cond0_desc = as.vector(cond0_desc[cond0_desc != 0])
(cond0_desc = mean(cond0_desc))

cond3_desc = cond3$pairwise$wadj[-23, ] 
cond3_desc = cond3_desc[, -23] 
cond3_desc = as.vector(cond3_desc[cond3_desc != 0])
(cond3_desc = mean(cond3_desc))

cond7_desc = cond7$pairwise$wadj[-23, ] 
cond7_desc = cond7_desc[, -23] 
cond7_desc = as.vector(cond7_desc[cond7_desc != 0])
(cond7_desc = mean(cond7_desc))

cond10_desc = cond10$pairwise$wadj[-23, ] 
cond10_desc = cond10_desc[, -23] 
cond10_desc = as.vector(cond10_desc[cond10_desc != 0])
(cond10_desc = mean(cond10_desc))

#signs: 
cond0_desc_s = na.omit(as.vector(cond0$pairwise$signs))
(sum(cond0_desc_s == -1)/2)
(sum(cond0_desc_s == 1)/2)

cond3_desc_s = na.omit(as.vector(cond3$pairwise$signs))
(sum(cond3_desc_s == -1)/2)
(sum(cond3_desc_s == 1)/2)

cond7_desc_s = na.omit(as.vector(cond7$pairwise$signs))
(sum(cond7_desc_s == -1)/2)
(sum(cond7_desc_s == 1)/2)

cond10_desc_s = na.omit(as.vector(cond10$pairwise$signs))
(sum(cond10_desc_s == -1)/2)
(sum(cond10_desc_s == 1)/2)
```

## CAN

```{r}
#fit
#CANFit <- IsingFit(issp_2019_can, gamma = 0.05)
CANFit <- IsingFit(issp_2019_can, gamma = 0.25)
```

```{r}
(small_w_is = NetworkToolbox::smallworldness(CANFit$weiadj, iter = 1000, 
          progBar = FALSE, method = c("TJHBL")))
```

```{r}
#plot
CANGraph<-qgraph(CANFit$weiadj, layout = averageLayout(GraphMGM),
            labels = shortnames_22, nodeNames = longnames_22,  
            groups = ggm_groups, color = ggm_colors, 
            label.scale = F, label.cex = 0.7,
            legend=T,  legend.cex = 0.30, theme = "Borkulo",
            borders = T, vsize=7.0, esize = 15, GLratio = 2,
            filetype="jpg", filename=here("Output", "Fig_4.1"))
```

```{r}
#descriptives
can_desc = as.vector(CANFit$weiadj)
length(can_desc[can_desc != 0])/462
```

```{r}
#centrality
centrality_can_graph = centralityPlot(CANGraph, labels = longnames_22, 
                                      orderBy = "Strength", 
                                      scale = "z-scores")

centrality_can_graph = centrality_can_graph +  
  geom_vline(xintercept=0, linetype="dotted") +
  scale_x_continuous(limits = c(-2,2.5), breaks = c(-2,-1,0,1,2)) +
  # theme_nice() +
  theme(axis.text.y=element_text(hjust=1))

ggsave(here("Output", "Fig_4.2.jpg"), centrality_can_graph,
        height = 4, width = 11)
```

```{r}
#combined centrality tables
centrality_combined = centralityPlot(list(GGM=GraphMGM,Ising=CANGraph), include = c("Strength"),
               scale = "z-scores", orderBy = "Strength") + 
  geom_vline(xintercept=0, linetype="dotted") +
  scale_x_continuous(limits = c(-2,2.8)) +
  # theme_nice() + 
  theme(axis.text.y=element_text(hjust=1))

ggsave(here("Output", "Supplement", "Fig1.jpg"), centrality_combined,
        height = 4)
```

```{r}
#Combined Figure_4

# Load the individual images
img1 <- image_read(here("Output", "Fig_4.1.jpg"))
img2 <- image_read(here("Output", "Fig_4.2.jpg"))

# Combine the images vertically
combined_img <- image_append(c(img1, img2), stack = TRUE)

# Save the combined image
image_write(combined_img, path = here("Output", "Fig_4.jpg"))
```

```{r}
# Save as PDF
image_write(combined_img, path = here("Output", "PDF", "Fig_4.pdf"), format = "pdf")

```


```{r}
#Save as EPS

# 4.1
# Open EPS device for the network graph
postscript(file = here("Output", "EPS", "Fig_4.1.eps"), 
           width = 10, height = 6, 
           horizontal = FALSE, 
           paper = "special", 
           onefile = FALSE)

# Network graph
CANGraph <- qgraph(
  CANFit$weiadj, 
  layout = averageLayout(GraphMGM),
  labels = shortnames_22, 
  nodeNames = longnames_22,  
  groups = ggm_groups, 
  color = ggm_colors, 
  label.scale = FALSE, 
  label.cex = 0.7,
  legend = TRUE,  
  legend.cex = 0.30, 
  theme = "Borkulo",
  borders = TRUE, 
  vsize = 7.0, 
  esize = 15, 
  GLratio = 2
)

# Close the EPS device
dev.off()

# 4.2
# Open EPS device for the centrality plot
postscript(file = here("Output", "EPS", "Fig_4.2.eps"), 
           width = 10, height = 3.5, 
           horizontal = FALSE, 
           paper = "special", 
           onefile = FALSE)

# Centrality plot
centrality_can_graph = centralityPlot(CANGraph, labels = longnames_22, 
                                      orderBy = "Strength", 
                                      scale = "z-scores") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_x_continuous(limits = c(-2, 2.5), breaks = c(-2, -1, 0, 1, 2)) +
  theme(axis.text.y = element_text(hjust = 1))

print(centrality_can_graph)

# Close the EPS device
dev.off()

```


## Simulation centrality

```{r}
#Simulation input 
SimInput <- LinTransform(CANFit$weiadj, CANFit$thresholds) #The LinTransform function rescales the edge weights and thresholds, so that a threshold of 0 indicates that a node has no disposition to be in a given state and a positive (negative) threshold indicates that a node has the disposition to be "on" ("off")

#create objects
shortnames_1 = shortnames_22[1]
shortnames_2 = shortnames_22[2]
shortnames_3 = shortnames_22[3]
shortnames_4 = shortnames_22[4]
shortnames_5 = shortnames_22[5]
shortnames_6 = shortnames_22[6]
shortnames_7 = shortnames_22[7]
shortnames_8 = shortnames_22[8]
shortnames_9 = shortnames_22[9]
shortnames_10 = shortnames_22[10]
shortnames_11 = shortnames_22[11]
shortnames_12 = shortnames_22[12]
shortnames_13 = shortnames_22[13]
shortnames_14 = shortnames_22[14]
shortnames_15 = shortnames_22[15]
shortnames_16 = shortnames_22[16]
shortnames_17 = shortnames_22[17]
shortnames_18 = shortnames_22[18]
shortnames_19 = shortnames_22[19]
shortnames_20 = shortnames_22[20]
shortnames_21 = shortnames_22[21]
shortnames_22 = shortnames_22[22]
```


```{r}
#samples with single nodes positive disposition
set.seed(123)

SampleNeg <- IsingSampler(3000, SimInput$graph, 
                          rep(-.1,22),#this argument specifies the thresholds, which are all set to -.1 
                          responses = c(-1L,1L))

Sample_1 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,0),
                            1,#this sets the thesholds of the first node to 1
                            rep(-.1,21)),#this sets the threshold of the others node to -.1
                            responses = c(-1L,1L))

Sample_2 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,1),#this sets the threshold of the first node to -.1
                            1,#this sets the thesholds of the second node to 1
                            rep(-.1,20)),#this sets the threshold of the others node to -.1
                            responses = c(-1L,1L))

Sample_3 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,2),
                            1,
                            rep(-.1,19)),
                            responses = c(-1L,1L))

Sample_4 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,3),
                            1,
                            rep(-.1,18)),
                            responses = c(-1L,1L))

Sample_5 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,4),
                            1,
                            rep(-.1,17)),
                            responses = c(-1L,1L))

Sample_6 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,5),
                            1,
                            rep(-.1,16)),
                            responses = c(-1L,1L))

Sample_7 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,6),
                            1,
                            rep(-.1,15)),
                            responses = c(-1L,1L))

Sample_8 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,7),
                            1,
                            rep(-.1,14)),
                            responses = c(-1L,1L))

Sample_9 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,8),
                            1,
                            rep(-.1,13)),
                            responses = c(-1L,1L))

Sample_10 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,9),
                            1,
                            rep(-.1,12)),
                            responses = c(-1L,1L))

Sample_11 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,10),
                            1,
                            rep(-.1,11)),
                            responses = c(-1L,1L))

Sample_12 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,11),
                            1,
                            rep(-.1,10)),
                            responses = c(-1L,1L))

Sample_13 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,12),
                            1,
                            rep(-.1,9)),
                            responses = c(-1L,1L))

Sample_14 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,13),
                            1,
                            rep(-.1,8)),
                            responses = c(-1L,1L))

Sample_15 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,14),
                            1,
                            rep(-.1,7)),
                            responses = c(-1L,1L))

Sample_16 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,15),
                            1,
                            rep(-.1,6)),
                            responses = c(-1L,1L))

Sample_17 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,16),
                            1,
                            rep(-.1,5)),
                            responses = c(-1L,1L))

Sample_18 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,17),
                            1,
                            rep(-.1,4)),
                            responses = c(-1L,1L))

Sample_19 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,18),
                            1,
                            rep(-.1,3)),
                            responses = c(-1L,1L))

Sample_20 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,19),
                            1,
                            rep(-.1,2)),
                            responses = c(-1L,1L))

Sample_21 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,20),
                            1,
                            rep(-.1,1)),
                            responses = c(-1L,1L))

Sample_22 <- IsingSampler(3000, SimInput$graph, 
                          c(rep(-.1,21),
                            1,
                            rep(-.1,0)),
                            responses = c(-1L,1L))

allsamples <- rbind(SampleNeg,
                    Sample_1,
                    Sample_2,
                    Sample_3,
                    Sample_4,
                    Sample_5,
                    Sample_6,
                    Sample_7,
                    Sample_8,
                    Sample_9,
                    Sample_10,
                    Sample_11,
                    Sample_12,
                    Sample_13,
                    Sample_14,
                    Sample_15,
                    Sample_16,
                    Sample_17,
                    Sample_18,
                    Sample_19,
                    Sample_20,
                    Sample_21,
                    Sample_22)

rowname <- rep(c('Baseline',
                 glue('Intervention on {shortnames_1}'),
                 glue('Intervention on {shortnames_2}'),
                 glue('Intervention on {shortnames_3}'),
                 glue('Intervention on {shortnames_4}'),
                 glue('Intervention on {shortnames_5}'),
                 glue('Intervention on {shortnames_6}'),
                 glue('Intervention on {shortnames_7}'),
                 glue('Intervention on {shortnames_8}'), 
                 glue('Intervention on {shortnames_9}'),
                 glue('Intervention on {shortnames_10}'),
                 glue('Intervention on {shortnames_11}'),
                 glue('Intervention on {shortnames_12}'),
                 glue('Intervention on {shortnames_13}'),
                 glue('Intervention on {shortnames_14}'),
                 glue('Intervention on {shortnames_15}'),
                 glue('Intervention on {shortnames_16}'),
                 glue('Intervention on {shortnames_17}'),
                 glue('Intervention on {shortnames_18}'), 
                 glue('Intervention on {shortnames_19}'),
                 glue('Intervention on {shortnames_20}'),
                 glue('Intervention on {shortnames_21}'),
                 glue('Intervention on {shortnames_22}')), 
               each=3000)

row.names(allsamples) <- rowname
```

```{r}
#calculate the sum scores of the different networks
sumSampleall<-apply(allsamples, 1, sum)  
sumscores<- data.frame(sumSampleall,rowname)
meansumscores<-aggregate(sumscores$sumSampleall, by=list(sumscores$rowname), mean)
sdsumscores<-aggregate(sumscores$sumSampleall, by=list(sumscores$rowname), sd)

graphicsumscores<- data.frame(meansumscores,sdsumscores)

#calculate confidence intervals for sumscore means
m<-graphicsumscores$x
s<-graphicsumscores$x.1
u<-m+1.96*s/sqrt(3000)
l<-m-1.96*s/sqrt(3000)

confi<- cbind(graphicsumscores, m, u, l)
names<-confi$Group.1
graph<-data.frame(confi,names)

graph$names <- factor(graph$names, levels = graph$names[order(graph$m)])
graph$names

#descriptives
confi_des = confi %>% 
  arrange(m) 
```

```{r}
#forestplot for the means of sumscores
mean_SampleNeg = meansumscores %>% 
  slice(1) %>% 
  pull(x)

upper_SampleNeg = u[1]

credplot.gg <- function(graph){
 require(ggplot2)
 p <- ggplot(graph, aes(x=names, y=m, ymin=l, ymax=u))+
 geom_pointrange()+
 geom_hline(yintercept = upper_SampleNeg, linetype="dashed")+
 geom_hline(yintercept = upper_SampleNeg+2, linetype="dotted")+
   scale_y_continuous(limits = c(-6,-1)) +
 coord_flip()+
 xlab('')+
   ylab('Mean sum scores')+
   theme_minimal()+
      theme(axis.text.y=element_text(hjust=1))
 return(p)
}

meansumscores_plot = credplot.gg(graph)

# jpg
ggsave(here("Output", "Fig_5.jpg"), meansumscores_plot, height = 4, width = 8)

# pdf
ggsave(here("Output", "PDF", "Fig_5.pdf"), meansumscores_plot, height = 4, width = 8,
       dpi = 600, 
       device = "pdf")

# Save as EPS
setEPS()
postscript(file = here("Output", "EPS", "Fig_5.eps"), 
           width = 8, height = 4, 
           horizontal = FALSE, 
           paper = "special", 
           onefile = FALSE)

print(meansumscores_plot)

# Close the EPS device
dev.off()

```

## Robustness

#### Edge accuracy ggm

```{r}
#edge weight accuracy: non parametric bootstrap with 8 cores
#edgeacc =  bootnet(issp_2019_nodes, nBoots = 10000, nCores = 8, 'EBICglasso')

#load the object instead:
load(here("Input", "bootstrap", "ggm_boot.RData"))

#plot
edgeacc_ggm = plot(edgeacc, labels = shortnames_22, order="sample")
ggsave(here("Output", "Supplement", "Fig_2.jpg"), edgeacc_ggm, height = 22, width = 15)

#summary edgeacc
saummary_edgeacc = summary(edgeacc, statistics = c("edge"), 
                            perNode = FALSE, rank = FALSE) 

#descriptives
summary_edgeacc_order <- saummary_edgeacc %>%
  arrange(mean)

summary_edgeacc_order <- saummary_edgeacc %>%
  filter(node1 == "work" | node2 == "work")
```

#### Centrality stability ggm

```{r}
#summary edgstr
saummary_edgstr = summary(edgeacc, statistics = c("strength"), 
                            perNode = FALSE, rank = FALSE) 
#descriptives
summary_edgstr_order = saummary_edgstr %>% 
  arrange(mean)

## Test: difference of strength of node 5 [conspiracy] vs 20 [hesitancy] (if the bootstrapped CI include 0, they do not differ)
test_strrr = differenceTest(edgeacc, 1, 3, "strength")
```

```{r}
# case dropping bootstrap
#centstab = bootnet(issp_2019_nodes, nBoots = 10000, 'EBICglasso', type = "case", nCores = 8)

#plot 
centstab_ggm = plot(centstab, "Strength", labels = shortnames_22)
ggsave(here("Output", "Supplement", "Fig_3.jpg"), centstab_ggm, height = 22, width = 15)

#CS-coefficient (result should be above 0.25, better if above 0.5)
corStability_ggm = corStability(centstab)
```

#### Testing Edge and centrality differences (for Results section)

```{r}
## Test: difference of weight ties 2-3 vs 4-5
#differenceTest(edgeacc, x = "p_inc_ineq", x2 = "b_red_pub", y = "p_inc_ineq", 
#                y2 = "j_ineq", "edge")

## Plot test results for every edge weight in the network
#pdf('../Output/robustness/test_edges.pdf', height = 70, width = 50)
#plot(edgeacc, "edge", plot = "difference", onlyNonZero = TRUE, order = "sample", 
#     labels = T)
#dev.off()
```

```{r}

#
## Plot test results for every edge weight in the network
#pdf('../Output/robustness/test_strenghts.pdf', height = 70, width = 50)
#plot(edgeacc, "strength", order = "mean", labels = T)
#dev.off()
```

### Stability of moderations 
```{r}
# #Stability of moderations
# #res_obj <- resample(object = mgm_mod, 
# #                    data = issp_2019_anger, 
# #                    nB = 500,
# #                    pbar = TRUE)
# 
# #load object instead
# load(here("Input", "bootstrap", "mod_boot.RData"))
# 
# #visualize result
# #png(here("Output", "Supplement", "Fig_4.1.png"), width = 3000, height = 3000)  # uncomment and # put table = F if you want figure rather than table
# tab_mod = data.frame(plotRes(res_obj, 
#         axis.ticks = c(-.1, 0, .1, .2, .3, .4, .5), 
#         axis.ticks.mod = c(-.1, -.05, 0, .05, .1), 
#         cex.label = 1, 
#         decreasing = TRUE,
#         labels = colnames(issp_2019_anger), 
#         layout.width.labels = 1,
#         table = TRUE))
# 
# #build a df
# tab_mod_df = tab_mod %>%
#   select(Variable.A, Variable.B, Mod_Mean, Mod_qtl_low, Mod_qtl_high, Mod_propLtZ) %>% 
#   filter(Mod_propLtZ>0.80) %>% #filtering moderation effect detected in more than 80% of # bootstrap samples
#   arrange(desc(Mod_Mean))
# 
# # Create the names_tab_mod vector
# names_tab_mod <- colnames(issp_2019_anger)
# 
# # Loop through the dataframe and replace numeric values with corresponding text
# tab_mod_df$Variable.A <- ifelse(tab_mod_df$Variable.A >= 1 
#                                    & tab_mod_df$Variable.A <= length(names_tab_mod),
#                                    names_tab_mod[tab_mod_df$Variable.A],
#                                    tab_mod_df$Variable.A)
# 
# tab_mod_df$Variable.B <- ifelse(tab_mod_df$Variable.B >= 1 
#                                    & tab_mod_df$Variable.B <= length(names_tab_mod),
#                                    names_tab_mod[tab_mod_df$Variable.B],
#                                    tab_mod_df$Variable.B)
# 
# write.csv(tab_mod_df, here("Output", "Supplement", "tab_mod_df.csv"), row.names = F)
# 
# write.csv(Orange_summ, "Orange_summ.csv", row.names = F)
```

#### Edge accuracy ising
```{r}
#edge weight accuracy: non parametric bootstrap with 8 cores
#edgeacc_is =  bootnet(issp_2019_can, nBoots = 10000, nCores = 8, 'IsingFit')

#load object instead
load(here("Input", "bootstrap", "is_boot.RData"))

#plot
edgeacc_is_plot = plot(edgeacc_is, labels = shortnames_22, order="sample")
ggsave(here("Output", "Supplement", "Fig_4.jpg"), edgeacc_is_plot, height = 22, width = 15)

#summary
saummary_edgeacc_is = summary(edgeacc_is, statistics = c("edge"), 
                            perNode = FALSE, rank = FALSE) 
#descriptives
summary_edg_is = saummary_edgeacc_is %>% 
  arrange(mean)

```


#### Centrality stability ising
```{r}
# case dropping bootstrap
#centstab_is = bootnet(issp_2019_can, nBoots = 10000, 'EBICglasso', type = "case", nCores = 8)

saummary_edgstr_is = summary(edgeacc_is, statistics = c("strength"), 
                            perNode = FALSE, rank = FALSE) 

#descriptives
summary_cent_is = saummary_edgstr_is %>% 
  arrange(mean)

test_strrr_is = differenceTest(edgeacc_is, 17, 12, "strength")
```


```{r}
#plot 
centstab_is_plot = plot(centstab, "Strength", labels = shortnames_22)
ggsave(here("Output", "Supplement", "Fig_5.jpg"), centstab_is_plot, height = 22, width = 15)

#CS-coefficient (result should be above 0.25, better if above 0.5)
corStability_is = corStability(centstab_is)
```

### Alternative dummy recode for ising

```{r}
#issp_2019_can = issp_2019_nodes %>% #truncation at 3
#  mutate(ineq_p= ifelse(ineq_p<=3,0,1),
#         reg_p= ifelse(reg_p<=3,0,1),
#         prog_b= ifelse(prog_b<=3,0,1),
#         ineq_j= ifelse(ineq_j<=2,0,1),
#         redis_d= ifelse(redis_d<=3,0,1),
#         redis_f= ifelse(redis_f<=3,0,1),
#         family= ifelse(family<=3,0,1),
#         edupar= ifelse(edupar<=3,0,1),
#         edu= ifelse(edu<=3,0,1),
#         work= ifelse(work<=3,0,1),
#         people= ifelse(people<=3,0,1),
#         connec= ifelse(connec<=3,0,1),
#         bribes= ifelse(bribes<=3,0,1),
#         race= ifelse(race<=3,0,1),
#         relig= ifelse(relig<=3,0,1),
#         sex= ifelse(sex<=3,0,1),
#         redis_p= ifelse(redis_p<=3,0,1),
#         redis_m= ifelse(redis_m<=3,0,1),
#         resp= ifelse(resp<=3,0,1),
#         train= ifelse(train<=3,0,1),
#         need= ifelse(need<=3,0,1),
#         merit= ifelse(merit<=3,0,1))

#issp_2019_can = issp_2019_nodes %>% #truncation at 2
#  mutate(ineq_p= ifelse(ineq_p<=2,0,1),
#         reg_p= ifelse(reg_p<=2,0,1),
#         prog_b= ifelse(prog_b<=2,0,1),
#         ineq_j= ifelse(ineq_j<=2,0,1),
#         redis_d= ifelse(redis_d<=2,0,1),
#         redis_f= ifelse(redis_f<=2,0,1),
#         family= ifelse(family<=2,0,1),
#         edupar= ifelse(edupar<=2,0,1),
#         edu= ifelse(edu<=2,0,1),
#         work= ifelse(work<=2,0,1),
#         people= ifelse(people<=2,0,1),
#         connec= ifelse(connec<=2,0,1),
#         bribes= ifelse(bribes<=2,0,1),
#         race= ifelse(race<=2,0,1),
#         relig= ifelse(relig<=2,0,1),
#         sex= ifelse(sex<=2,0,1),
#         redis_p= ifelse(redis_p<=2,0,1),
#         redis_m= ifelse(redis_m<=2,0,1),
#         resp= ifelse(resp<=2,0,1),
#         train= ifelse(train<=2,0,1),
#         need= ifelse(need<=2,0,1),
#         merit= ifelse(merit<=2,0,1))
```


# Output
```{r}
#Save heavy objects
save(edgeacc, centstab,
     file = here("Input", "bootstrap", "ggm_boot.RData"))

#save(res_obj,
#     file = here("Input", "bootstrap", "mod_boot.RData"))

save(edgeacc_is, centstab_is,
     file = here("Input", "bootstrap", "is_boot.RData"))
```

